---
title: This Article Looks Quite Authoritative
author: Julie Norman
output: pdf_document
---

```{r load_libraries, echo=F, include=F}
library(tidyverse)
library(stargazer)
```

```{r load_data, echo=F, include=F}
#load and clean data
data <- read_csv("../data/original_yougov.csv") %>%
  rename(moral_just = ucl_1_1, strategic = ucl_1_2, terrorism = ucl_1_3) %>%
  mutate(
  casualties = experiment_split %in% c(2,4,6,8,10,12),
  conservative_action = experiment_split %in% c(1,2,5,6,9,10),
    experiment_split = experiment_split %>%
      dplyr::recode(
        `1` = "Abortion advocacy, no injuries",
        `2` = "Abortion advocacy, casualties",
        `3` = "Abortion restriction, no injuries",
        `4` = "Abortion restriction, casualties",
        `5` = "Environmental advocacy, no injuries",
        `6` = "Environmental advocacy, casualties",
        `7` = "Fossil fuel advocacy, no injuries",
        `8` = "Fossil fuel advocacy, casualties",
        `9` = "Immigration advocacy, no injuries",
        `10` = "Immigration advocacy, casualties",
        `11` = "Immigration restriction, no injuries",
        `12` = "Immigration restriction, casualties"
      ),
    pid3 = pid3 %>%
      dplyr::recode_factor(
        `4` = "Other",
        `5` = "Not Sure",
        `1` = "Democrat",
        `2` = "Republican",
        `3` = "Independent",
      ),
    region = region %>%
      dplyr::recode(
        `1` = "Northeast",
        `2` = "Midwest",
        `3` = "South",
        `4` = "West"
      ),
    vote = presvote20post %>%
      dplyr::recode_factor(
        `6` = "Did not vote",
        `1` = "Joe Biden",
        `2` = "Donald Trump",
        `3` = "Jo Jorgensen",
        `4` = "Howie Hawkins",
        `5` = "Other"
      ),
    race = race %>%
      dplyr::recode_factor(
        `1` = "White",
        `2` = "Black",
        `3` = "Hispanic",
        `4` = "Other (NET)"
      ),
    educ = educ %>%
      dplyr::recode_factor(
        `1` = "No HS",
        `2` = "High school graduate",
        `3` = "Some college",
        `4` = "2-year",
        `5` = "4-year",
        `6` = "Postgrad",
        .ordered = TRUE
    ),
    female = gender == 2,
    gender = gender %>%
        recode(
        `1` = "Male",
        `2` = "Female",
       ),
    profile_gross_household_num = profile_gross_household,
    profile_gross_household = profile_gross_household %>%
        recode_factor(
        `1` = "[0,10,000)",
        `2` = "[10k,20k)",
        `3` = "[20k,30k)",
        `4` = "[30k,40k)",
        `5` = "[40k,50k)",
        `6` = "[50k,60k)",
        `7` = "[60k,70k)",
        `8` = "[70k,80k)",
        `9` = "[80k,100k)",
        `10` = "[100k,120k)",
        `11` = "[120k,150k)",
        `12` = "[150k,200k)",
        `13` = "[200k,250k)",
        `14` = "[250k,350k)",
        `15` = "[350k,500k)",
        `16` = "[500k,Inf)",
        `98` = "Don't know",
        `99` = "Prefer not to answer",
        .ordered = TRUE
      ),
	factor_ideo5 =
		case_when(
				  ideo5 <=2 ~ "Liberal / V. Liberal",
				  ideo5 == 3 ~ "Moderate",
				  ideo5 %in% c(4,5) ~ "Conservative / V. Conservative",
				  ideo5 == 6 ~ "Not Sure",
				  ) %>%
	factor() %>% relevel(ref="Moderate"),
	ide05 = na_if(ideo5, 6)-3,
    moral_just = -1*(moral_just-4),
    strategic = -1*(strategic-4),
    terrorism = -1*(terrorism-4)
  )
```

# Variables

In this section I describe the variables used in the analysis.  I provide a
table of summary statistics for the continuous and dummy variables used in the
analysis below.

Responses to the questions "is this action terrorism?", "was this action
morally justified?", and "was this action strategic?" were originally
collected on a 1-7 scale, where 1 indicated strong agreement and 7 indicated
strong disagreement.  I rescale responses to between -3 and 3, where -3 now
indicates strong disagreement, 0 indicates a neutral answer, and 3 indicates
strong agreement.

Respondents were asked to identify their ideology as either "Very Liberal,"
"Liberal," "Moderate," "Conservative," "Very Conservative," or "Don't
Know." For analyses involving respondents' ideology, I remove "Don't Know"
and scale answers to a -2-2 scale, where -2 indicates a very liberal
respondent, and +2 indicates a very Conservative respondent.


```{r summary_statistics, results= "asis", echo=F}
# Create tables of summary statistics
data %>%
select(ideo5,moral_just,strategic, terrorism, conservative_action, female,casualties) %>%
rename("Ideology" = "ideo5",
	   "Moral Justifiaction" = "moral_just",
	   "Strategic"="strategic",
	   "Terroism" = "terrorism",
	   "Conservative Action" = "conservative_action",
	   "Female"="female",
	   "Casualties"="casualties") %>%
data.frame()  %>%
stargazer(header=F)
```

## Ideology on Moral Justification

First, I examine the relationship between a respondent's ideology and their
views of the actions as morally justifiable.  There is a significant positive
relationship between a respondent's ideology on a five point scale and
perceptions of moral justifiability indicating that *ceretis paribus*,
conservatives rated the actions as more justifiable than liberals or moderates.

The interactions between an action being conservative and a respondent's
ideology are uniformly significant and positive, indicating that respondents
that are more conservative see conservative actions as significantly more
justifiable than liberal actions, and vice versa.

```{r idology_moral_responsibility, results= "asis", echo=F}
# ideology on moral justifiability
i_moral_just1 <- lm(moral_just ~ ideo5, data = data, weights = weight_pol)
i_moral_just2 <- lm(moral_just ~ ideo5 + conservative_action, data = data, weights = weight_pol)
i_moral_just3 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
i_moral_just4 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
i_moral_just5 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
i_moral_just6 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(i_moral_just1, i_moral_just2, i_moral_just3, i_moral_just4, i_moral_just5, i_moral_just6,
    title="Ideology vs Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
	covariate.labels =
	  c("Ideology", "Conservative Action","Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Ideology $\\times$ conserv. act.",
	   "Intercept"),
    df=F,
	header=F,
    label = "p_moral_just"
)
```

## Ideology on strategy
In this section, I investigate the relationships between a respondent's
ideology on a five point scale, and their views of the actions as strategic.

The relationships between ideology and views of the actions as strategic are
positive and significant when controlling for the interaction between ideology
and whether the action was in favor of a conservative cause.  This indicates,
that across the board, more conservative respondents also saw the actions as
more justified.

```{r ideology_strategic, results= "asis", echo=F}
# Ideology on Strategic
i_strategic1 <- lm(strategic ~ ideo5, data = data, weights = weight_pol)
i_strategic2 <- lm(strategic ~ ideo5 + conservative_action, data = data, weights = weight_pol)
i_strategic3 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
i_strategic4 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
i_strategic5 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
i_strategic6 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(i_strategic1, i_strategic2, i_strategic3, i_strategic4,i_strategic5,i_strategic6,
    title="Ideology Vs Perceptions of Actions as Strategic",
    dep.var.labels = c("Action is strategic"),
	covariate.labels = c("Ideology", "Conservative Action","Casualties",
		"Female","Black", "Hispanic","Race --- other",
		"Ideology $\\times$ conserv. act.",
		"Intercept"),
    df=F,
	header=F,
    label="p_strategic"
)
```

## Ideology on Perceptions of actions as terrorism

In this section, I investigate the relationships between Ideology on a
five-point scale, and perceptions of the actions as terrorism.

Across all of the models, moving a respondent rightwards along the ideology
scale is associated with a decrease in their agreement of the actions as
terrorism, suggesting that more conservative respondents identify the actions
as less terroristic.  The interactions between ideology and an action being
conservative are significant and negative, indicating that conservatives are
much less ready to identify conservative actions as terrorism, and vice versa.

```{r ideology_terrorism, results= "asis", echo=F}
# ideology on Terrorism
 i_terrorism1 <- lm(terrorism ~ ideo5, data = data, weights = weight_pol)
 i_terrorism2 <- lm(terrorism ~ ideo5 + conservative_action, data = data, weights = weight_pol)
 i_terrorism3 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
 i_terrorism4 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
 i_terrorism5 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
 i_terrorism6 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(i_terrorism1, i_terrorism2, i_terrorism3, i_terrorism4, i_terrorism5, i_terrorism6,
	title="Estimates of Effect of Partisanship on Terrorism",
	dep.var.labels = c("Action is terrorism"),
	covariate.labels =
		c("Ideology", "Conservative Action","Casualties",
		"Female","Black", "Hispanic","Race --- other",
		"Ideology $\\times$ conserv. act.",
		"Intercept"),
	df=F,
	header=F,
	label="p_terrorism"
)
```

## Ideology on Moral Justification

```{r idology_2_moral_responsibility, results= "asis", echo=F}
# ideology on moral justifiability
i_moral_just1 <- lm(moral_just ~ factor_ideo5, data = data, weights = weight_pol)
i_moral_just2 <- lm(moral_just ~ factor_ideo5 + conservative_action, data = data, weights = weight_pol)
i_moral_just3 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action, data = data, weights = weight_pol)
i_moral_just4 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties, data = data, weights = weight_pol)
i_moral_just5 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
i_moral_just6 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(i_moral_just1, i_moral_just2, i_moral_just3, i_moral_just4, i_moral_just5, i_moral_just6,
    title="Ideology vs Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
	covariate.labels =
	  c("Ideology", "Conservative Action","Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Ideology $\\times$ conserv. act.",
	   "Intercept"),
    df=F,
	header=F,
    label = "p_moral_just"
)
```


<!---
## Partisanship on Moral Justifiability

I investigate the relationship of partisanship on perceptions of moral
justifiability, perceptions of an action as terrorism, and ratings of the
strategic usefulness of the action. As a note, the reference category for the
partisan affiliation variable is "affiliated with another party.''

## Partisanship on moral justifiability

Using a linear regression, I differences in identifying the actions as
justifiable between Republicans, Democrats, independent voters, and respondents
unsure of their partisanship relative to respondents who identify with another
party.  The results of this analysis can be seen in \autoref{p_moral_just}

I allow interactions between the effect of partisanship and whether the action
the respondent was asked about aligns with a traditionally conservative or
traditionally liberal cause.  This allows for the possibility that
Democrat-identifying respondents could be more likely to identify actions that
identify with a Republican/conservative cause as justified, and vice versa.

Across all model specifications, I find no association between a respondent
identifying as a Republican, Democrat, or Independent and their opinions of the
actions as justified.  Respondents identifying as unsure of their partisan
affiliation rate the actions as more justified, across all models.

The interactions between partisan affiliation and the ideological slant of the
actions are insignificant across all models, indicating that democrats are not
more likely to view actions in support of traditionally liberal causes as
justifiable when compared to respondents who identified with a party not
directly asked about in the survey.  The same can be said with respect to
Republicans and traditionally republican causes.

```{r, results= "asis", echo=F}
# Partisanship on Moral Justifiability
moral_just1 <- lm(moral_just ~ pid3, data = data, weights = weight_pol)
moral_just2 <- lm(moral_just ~ pid3 + conservative_action, data = data, weights = weight_pol)
moral_just3 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
moral_just4 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
moral_just5 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
moral_just6 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(moral_just1, moral_just2, moral_just3, moral_just4, moral_just5, moral_just6,
    title="Estimates of Effect of Partisanship on Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
	table.placement = "ht!",
    df=F,
	header=F,
    label = "p_moral_just"
)
```

## Effects of Partisanship on Perceptions of Actions as Strategic

In this section I test for differences in identifying actions as strategic
between Democratic, Republican, and Independent-identifying respondents
relative to respondents who chose another party.

```{r, results= "asis", echo=F}
# Partisanship on Strategic
strategic1 <- lm(strategic ~ pid3, data = data, weights = weight_pol)
strategic2 <- lm(strategic ~ pid3 + conservative_action, data = data, weights = weight_pol)
strategic3 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
strategic4 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
strategic5 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
strategic6 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(strategic1, strategic2, strategic3, strategic4,strategic5,strategic6,
    title="Estimates of Effect of Partisanship on Strategic",
    dep.var.labels = c("Action is strategic"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
	table.placement = "ht!",
    df=F,
	header=F,
    label="p_strategic"
)
```

Across all models, there is a significant negative relationship between a
respondent identifying as a Republican, Democrat, or independent.  This means
that respondents identifying with these parties tended
to rate the actions as less strategic than respondents who identified with
another party, even when controlling for the effects of race and gender.

Once again, I allow for interactions between the ideological slant of an action
and the effects of partisanship, finding no significant association.  This
means that the models do not predict any difference between Republicans /
Democrats responding to a traditionally conservative / liberal action when
compared to respondents who identify with another party.

The relationship between casualties and perceptions of the actions as strategic
is uniformly negative across all models.  As the presence of casualties was
fully randomized, we can conclude that the presence of casualties directly
results in respondents rating the action as less strategic.

## Partisanship on Perception of Actions as Terrorism

In this section I test for differences in identifying actions as terrorism
between Democratic, Republican, and Independent-identifying respondents
relative to respondents who chose another party.


```{r, results= "asis", echo=F}
# Partisanship on Terrorism
terrorism1 <- lm(terrorism ~ pid3, data = data, weights = weight_pol)
terrorism2 <- lm(terrorism ~ pid3 + conservative_action, data = data, weights = weight_pol)
terrorism3 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
terrorism4 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
terrorism5 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
terrorism6 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(terrorism1, terrorism2, terrorism3, terrorism4, terrorism5, terrorism6,
    title="Estimates of Effect of Partisanship on Terrorism",
    dep.var.labels = c("Action is terrorism"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
    df=F,
	table.placement = "ht!",
	header=F,
    label="p_terrorism"
)
```

Across all models, there is a significant positive relationship between
respondents identifying as Democrats, and their rating the actions as
terrorism. This suggests that all else equal, Democratic respondents rated the
actions as terrorism more than those in the reference category, respondents who
identified as affiliated with a party not surveyed.
--->
