---
title: This Article Looks Quite Authoritative
author: Author Name
output: pdf_document
urlcolor: blue
---

```{r load_libraries, echo=F, include=F}
# This code loads the libraries used in the analysis into memory
library(tidyverse)
library(stargazer)
```

```{r load_data, echo=F, include=F}
# This section loads the data from the original survey and recodes and
# transforms the variables into the ones used in the paper

data <- read_csv("../data/original_yougov.csv") %>%
  rename(moral_just = ucl_1_1, strategic = ucl_1_2, terrorism = ucl_1_3) %>%
  mutate(
  casualties = experiment_split %in% c(2,4,6,8,10,12),
  conservative_action = experiment_split %in% c(1,2,5,6,9,10),
    experiment_split = experiment_split %>%
      dplyr::recode(
        `1` = "Abortion advocacy, no injuries",
        `2` = "Abortion advocacy, casualties",
        `3` = "Abortion restriction, no injuries",
        `4` = "Abortion restriction, casualties",
        `5` = "Environmental advocacy, no injuries",
        `6` = "Environmental advocacy, casualties",
        `7` = "Fossil fuel advocacy, no injuries",
        `8` = "Fossil fuel advocacy, casualties",
        `9` = "Immigration advocacy, no injuries",
        `10` = "Immigration advocacy, casualties",
        `11` = "Immigration restriction, no injuries",
        `12` = "Immigration restriction, casualties"
      ),
    pid3 = pid3 %>%
      dplyr::recode_factor(
        `4` = "Other",
        `5` = "Not Sure",
        `1` = "Democrat",
        `2` = "Republican",
        `3` = "Independent",
      ),
    region = region %>%
      dplyr::recode(
        `1` = "Northeast",
        `2` = "Midwest",
        `3` = "South",
        `4` = "West"
      ),
    vote = presvote20post %>%
      dplyr::recode_factor(
        `6` = "Did not vote",
        `1` = "Joe Biden",
        `2` = "Donald Trump",
        `3` = "Jo Jorgensen",
        `4` = "Howie Hawkins",
        `5` = "Other"
      ),
    race = race %>%
      dplyr::recode_factor(
        `1` = "White",
        `2` = "Black",
        `3` = "Hispanic",
        `4` = "Other (NET)"
      ),
    educ = educ %>%
      dplyr::recode_factor(
        `1` = "No HS",
        `2` = "High school graduate",
        `3` = "Some college",
        `4` = "2-year",
        `5` = "4-year",
        `6` = "Postgrad",
        .ordered = TRUE
    ),
    female = gender == 2,
    gender = gender %>%
        recode(
        `1` = "Male",
        `2` = "Female",
       ),
    profile_gross_household_num = profile_gross_household,
    profile_gross_household = profile_gross_household %>%
        recode_factor(
        `1` = "[0,10,000)",
        `2` = "[10k,20k)",
        `3` = "[20k,30k)",
        `4` = "[30k,40k)",
        `5` = "[40k,50k)",
        `6` = "[50k,60k)",
        `7` = "[60k,70k)",
        `8` = "[70k,80k)",
        `9` = "[80k,100k)",
        `10` = "[100k,120k)",
        `11` = "[120k,150k)",
        `12` = "[150k,200k)",
        `13` = "[200k,250k)",
        `14` = "[250k,350k)",
        `15` = "[350k,500k)",
        `16` = "[500k,Inf)",
        `98` = "Don't know",
        `99` = "Prefer not to answer",
        .ordered = TRUE
      ),
	factor_ideo5 =
		case_when(
				  ideo5 <=2 ~ "(V.) Liberal",
				  ideo5 == 3 ~ "Moderate",
				  ideo5 %in% c(4,5) ~ "(V.) Conservative",
				  ideo5 == 6 ~ "Not Sure",
				  ) %>%
	factor() %>% relevel(ref="Moderate"),
	ide05 = na_if(ideo5, 6)-3,
    moral_just = -1*(moral_just-4),
    strategic = -1*(strategic-4),
    terrorism = -1*(terrorism-4)
  )
```

# Tools

To streamline editing and minimize errors, I have written this document in
[Rmarkdown](https://rmarkdown.rstudio.com/).  So that others can edit this
document without having to install a working version of R, I provide a [docker
image](https://www.docker.com/) which will run R and compile the document in a
container.

Documentation for working with Rmarkdown can be found [here](https://bookdown.org/yihui/rmarkdown/).

Docker documentation can be found [here](https://docs.docker.com/).

# Variables

In this section I describe the variables used in the analysis.  I provide a
table of summary statistics for the continuous and dummy variables used in the
analysis below.

Responses to the questions "is this action terrorism?", "was this action
morally justified?", and "was this action strategic?" were originally
collected on a 1-7 scale, where 1 indicated strong agreement and 7 indicated
strong disagreement.  I rescale responses to between -3 and 3, where -3 now
indicates strong disagreement, 0 indicates a neutral answer, and 3 indicates
strong agreement.

In the original YouGov survey, respondents were asked to identify their
ideology as either "Very Liberal," "Liberal," "Moderate," "Conservative," "Very
Conservative," or "Don't Know."

For analyses involving respondents' ideology, I operationalize ideology using
both a categorical measure and an interval level measure.  The categorical
measure of ideology recovers the effect of switching a respondent from one
ideology to another (i.e, switching from moderate to liberal), while the
interval-level measurement recovers the average effect of a moving a respondent
one space up or down the ideology scale.  To construct the categorical
measurement of ideology, I code respondents as either Liberal if they recorded
their ideology as "very liberal or "liberal", moderate if they described
themselves as moderates, conservative if they described themselves as somewhat
or very conservative, and "not sure" as they reported being unsure about which
category they fit into.  I set the reference level in these analyses as
"Moderate." For the interval-level measure, I remove "Don't Know" and scale
answers to a -2-2 scale, where -2 indicates a very liberal respondent, and +2
indicates a very Conservative respondent.


```{r summary_statistics, results= "asis", echo=F}
# Create tables of summary statistics
data %>%
select(ideo5,moral_just,strategic, terrorism, conservative_action, female,casualties) %>%
rename("Ideology" = "ideo5",
	   "Moral Justification" = "moral_just",
	   "Strategic"="strategic",
	   "Terrorism" = "terrorism",
	   "Conservative Action" = "conservative_action",
	   "Female"="female",
	   "Casualties"="casualties") %>%
data.frame()  %>%
stargazer(header=F, digits=2)
```

# Ideology on Moral Justification

First, I examine the relationship between a respondent's ideology and their
views of the actions as morally justifiable.  There is a significant positive
relationship between a respondent's ideology on a five point scale and
perceptions of moral justifiability indicating that *ceretis paribus*,
conservatives rated the actions as more justifiable than liberals or moderates.

The interactions between an action being conservative and a respondent's
ideology are uniformly significant and positive, indicating that respondents
that are more conservative see conservative actions as significantly more
justifiable than liberal actions, and vice versa.

```{r idology_moral_responsibility, results= "asis", echo=F}
# Estimates relationships between ideology and perceptions of moral
# justifiability with an interval measure of ideology
ideo_moral1 <- lm(moral_just ~ ideo5, data = data, weights = weight_pol)
ideo_moral2 <- lm(moral_just ~ ideo5 + conservative_action, data = data, weights = weight_pol)
ideo_moral3 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
ideo_moral4 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
ideo_moral5 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
ideo_moral6 <- lm(moral_just ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(ideo_moral1, ideo_moral2, ideo_moral3, ideo_moral4, ideo_moral5, ideo_moral6,
    title="Ideology vs Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
	covariate.labels =
	  c("Ideology", "Conservative Action","Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Ideology $\\times$ conserv. act.",
	   "Intercept"),
    df=F,
	digits = 2,
	header=F,
    label = "p_moral_just"
)
```

## Categorical Measure

In this section, I investigate the relationship between ideology and
perceptions of the actions as morally justifiability.

Surprisingly, there is no significant relationship between the presence of
casualties and perceptions of moral justifiability, indicating that the
presence of casualties had no effect on perceptions of moral justifiability
*ceritis paribus*.

Across all models, the estimate of the affect associated with an action being
conservative is significant and negative indicating that among moderate
respondents, an action being conservative was associated with a decrease in
perceptions of it as moral justifiability.

Across all models, there is a significant positive interaction between the
conservative action term and the conservative respondent term indicating that
relative to moderate respondents, conservatives found conservative actions more
justified.  There is no significant interaction between the liberal respondent
and conservative action terms, indicating that liberal respondents did not
react significantly differently to conservative / liberal actions than moderate
respondents.



```{r iedology_2_moral_responsibility, results= "asis", echo=F}
# Estimates effects of ideology on perceptions of moral justifiability, using a
# categorical measure of ideology
factor_ideo_moral1 <- lm(moral_just ~ factor_ideo5, data = data, weights = weight_pol)
factor_ideo_moral2 <- lm(moral_just ~ factor_ideo5 + conservative_action, data = data, weights = weight_pol)
factor_ideo_moral3 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action, data = data, weights = weight_pol)
factor_ideo_moral4 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties, data = data, weights = weight_pol)
factor_ideo_moral5 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
factor_ideo_moral6 <- lm(moral_just ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(factor_ideo_moral1, factor_ideo_moral2, factor_ideo_moral3, factor_ideo_moral4, factor_ideo_moral5, factor_ideo_moral6,
    title="Ideology vs Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
	  covariate.labels = c("Conservative", "Liberal","Not Sure",
		"C. Action","Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Conservative $\\times$ C. Action",
	   "Liberal $\\times$ C. Action",
	   "Not Sure $\\times$ C. Action",
	   "Intercept"),
    df=F,
	header=F,
	digits = 2,
    label = "p_moral_just"
)
```

## Effects Graph
```{r, message=F,echo=F}
data %>%
	ggplot(aes(x=conservative_action, y=moral_just, group=factor_ideo5, linetype=factor_ideo5)) +
	geom_smooth(aes(weight=weight_pol), col="black", method="lm") +
	ggtitle("Interaction Effects of Ideology / Conservative Action on Perception\nOf Moral Justification") +
	ylab("Moral Justification\n(Higher Scores Mean More Justified)") +
	xlab("Action type") +
	scale_x_discrete(labels=c( "FALSE" = "Liberal", "TRUE" = "Conservative")) +
	labs(linetype = "Respondent ideology") +
	theme_classic()

ggsave("../charts/partisanship_justification.png")

```

## Effects of Casualties
```{r, message=F,echo=F}
data %>%
	ggplot(aes(x=casualties, y=moral_just, group="hey")) +
	geom_smooth(aes(weight=weight_pol), col = "black", method="lm") +
	ggtitle("Relationship between Casualties on Perceptions\nOf Strategy") +
	ylab("Moral Justification\n(Higher Scores Mean More Justified)") +
	xlab("Action Caused Casualties") +
	theme_classic()

ggsave("../charts/casualties_justification.png")
```


# Ideology on Strategy
## Interval Measure

In this section, I investigate the relationships between a respondent's
ideology on a five point scale, and their views of the actions as strategic.

Across all models, there is a significant negative relationship between an
action resulting in casualties and perceptions of it as strategic indicating
that holding all other factors constant, an action resulting in causalities was
associated with lower perceptions of it as strategic, relative to an identical
action that did not produce casualties.

When controlling for the interaction between respondents' ideologies and an
action being conservative, there is a positive relationship between ideology on
a five-point scale and perceptions of the actions as strategic.  This indicates
more conservative respondents saw the actions as more justified *ceritis
paribus*.  Insignificant interactions between the respondent ideology term and
the conservative action indicates that a respondent's ideology does not
influence the effect that an action being liberal conservative has on their
view of it as strategic.

```{r ideology_strategic, results= "asis", echo=F}
# Estimates effects of ideology on perceptions of the actions as strategic,
# using an interval-level measure of ideology

ideo_strategic1 <- lm(strategic ~ ideo5, data = data, weights = weight_pol)
ideo_strategic2 <- lm(strategic ~ ideo5 + conservative_action, data = data, weights = weight_pol)
ideo_strategic3 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
ideo_strategic4 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
ideo_strategic5 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
ideo_strategic6 <- lm(strategic ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(ideo_strategic1, ideo_strategic2, ideo_strategic3, ideo_strategic4,ideo_strategic5,ideo_strategic6,
    title="Ideology Vs Perceptions of Actions as Strategic",
    dep.var.labels = c("Action is strategic"),
	covariate.labels = c("Ideology", "Conservative Action","Casualties",
		"Female","Black", "Hispanic","Race --- other",
		"Ideology $\\times$ conserv. act.",
		"Intercept"),
    df=F,
	header=F,
	digits = 2,
    label="p_strategic"
)
```

## Categorical Measure

In this section, I analyze the effects of ideology on perceptions of the
strategic usefulness of an action using a categorical measurement of ideology.
Again, The reference level for this measure is "moderate."

The coefficient associated with a respondent being liberal is significant and
negative across all models, indicating that relative to moderate respondents,
liberals saw all actions as less justified.  The coefficient associated with a
respondent being conservative is not significant across all models indicating
that there were no significant differences between how conservative respondents
and moderate respondents perceived the actions as strategic.  Insignificant
interactions between the ideology variables indicate that a respondents
ideology does not influence how they react to an action being conservative /
liberal.

```{r factor_ideology_strategic, results= "asis", echo=F}
# Estimates effects of ideology on perceptions of the actions as strategic,
# using a categorical measure of ideology

factor_ideo_strategic1 <- lm(strategic ~ factor_ideo5, data = data, weights = weight_pol)
factor_ideo_strategic2 <- lm(strategic ~ factor_ideo5 + conservative_action, data = data, weights = weight_pol)
factor_ideo_strategic3 <- lm(strategic ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action, data = data, weights = weight_pol)
factor_ideo_strategic4 <- lm(strategic ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties, data = data, weights = weight_pol)
factor_ideo_strategic5 <- lm(strategic ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
factor_ideo_strategic6 <- lm(strategic ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(factor_ideo_strategic1, factor_ideo_strategic2, factor_ideo_strategic3, factor_ideo_strategic4,factor_ideo_strategic5,factor_ideo_strategic6,
    title="Ideology Vs Perceptions of Actions as Strategic",
    dep.var.labels = c("Action is strategic"),
	  covariate.labels = c("Conservative", "Liberal","Not Sure",
		"C. Action","Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Conservative $\\times$ C. Action",
	   "Liberal $\\times$ C. Action",
	   "Not Sure $\\times$ C. Action",
	   "Intercept"),
    df=F,
	header=F,
	digits = 2,
    label="p_strategic"
)

```

## Effects Graph
```{r, message=F,echo=F}
data %>%
	ggplot(aes(x=conservative_action, y=strategic, group=factor_ideo5, linetype=factor_ideo5)) +
	geom_smooth(aes(weight=weight_pol), col="black", method="lm") +
	ggtitle("Interaction Effects of Ideology / Conservative Action on Perceptions\nOf Strategy") +
	ylab("Perceptions of Strategy \n(Higher Scores Mean More Strategic)") +
	xlab("Action type") +
	scale_x_discrete(labels=c( "FALSE" = "Liberal", "TRUE" = "Conservative")) +
	labs(linetype = "Respondent ideology") +
	theme_classic()

ggsave("../charts/partisanship_strategy.png")
```

## Effects of Casualties
```{r, message=F,echo=F}
data %>%
	ggplot(aes(x=casualties, y=strategic, group="hey")) +
	geom_smooth(aes(weight=weight_pol), col = "black", method="lm") +
	ggtitle("Relationship between Casualties on Perceptions\nOf Strategy") +
	ylab("Moral Justification\n(Higher Scores Mean More Justified)") +
	xlab("Action Caused Casualties") +
	theme_classic()

ggsave("../charts/casualties_strategy.png")
```

# Ideology on Perceptions of Actions as Terrorism

## Interval Measure

In this section, I investigate the relationships between Ideology measured on a
five-point scale, and perceptions of the actions as terrorism.

Across all of the models, moving a respondent rightwards along the ideology
scale is associated with a decrease in their agreement of the actions as
terrorism, suggesting that more conservative respondents identify the actions
as less terroristic.  The interactions between ideology and an action being
conservative are significant and negative, indicating that conservatives are
much less ready to identify conservative actions as terrorism, and vice versa.
This is a substantively large effect - one step along the ideology scale
corresponds to the same difference in perceptions associated with an action
causing casualties. This fact is even more striking when considering that the
standard deviation of the ideology measurement 1.49.

```{r ideology_terrorism, results= "asis", echo=F}
# Measures relationships between ideology and perceptions of actions as
# terrorism, using an interval-level measure of ideology

 ideo_terrorism1 <- lm(terrorism ~ ideo5, data = data, weights = weight_pol)
 ideo_terrorism2 <- lm(terrorism ~ ideo5 + conservative_action, data = data, weights = weight_pol)
 ideo_terrorism3 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action, data = data, weights = weight_pol)
 ideo_terrorism4 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties, data = data, weights = weight_pol)
 ideo_terrorism5 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
 ideo_terrorism6 <- lm(terrorism ~ ideo5 + conservative_action + ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(ideo_terrorism1, ideo_terrorism2, ideo_terrorism3, ideo_terrorism4, ideo_terrorism5, ideo_terrorism6,
	title="Estimates of Effect of Ideology on Terrorism",
	dep.var.labels = c("Action is terrorism"),
	covariate.labels =
		c("Ideology", "C. Action","Casualties",
		"Female","Black", "Hispanic","Race --- other",
		"Ideology $\\times$ C. act.",
		"Intercept"),
	df=F,
	header=F,
	digits = 2,
	label="p_terrorism"
)
```

## Categorical Measure

In this section, I investigate the relationships between the categorical
measure of ideology five-point scale, and perceptions of the actions as
terrorism.

```{r factor_ideology_terrorism, results= "asis", echo=F}
# Measures relationships between ideology and perceptions of actions as
# terrorism, using a categorical measure of ideology

 factor_ideo_terrorism1 <- lm(terrorism ~ factor_ideo5, data = data, weights = weight_pol)
 factor_ideo_terrorism2 <- lm(terrorism ~ factor_ideo5 + conservative_action, data = data, weights = weight_pol)
 factor_ideo_terrorism3 <- lm(terrorism ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action, data = data, weights = weight_pol)
 factor_ideo_terrorism4 <- lm(terrorism ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties, data = data, weights = weight_pol)
 factor_ideo_terrorism5 <- lm(terrorism ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female, data = data, weights = weight_pol)
 factor_ideo_terrorism6 <- lm(terrorism ~ factor_ideo5 + conservative_action + factor_ideo5:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(factor_ideo_terrorism1, factor_ideo_terrorism2, factor_ideo_terrorism3, factor_ideo_terrorism4, factor_ideo_terrorism5, factor_ideo_terrorism6,
	title="Estimates of Effect of Ideology on Terrorism",
	dep.var.labels = c("Action is terrorism"),
	  covariate.labels = c("Conservative", "Liberal","Not Sure",
		"C. Action", "Casualties",
	   "Female","Black", "Hispanic","Race --- other",
	   "Conservative $\\times$ C. Action",
	   "Liberal $\\times$ C. Action",
	   "Not Sure $\\times$ C. Action",
	   "Intercept"),
	df=F,
	header=F,
	digits = 2,
	label="p_terrorism"
)
```

Across all models the coefficient associated with casualties is positive
indicating that respondents of all groups found actions that resulted in
casualties to be more terroristic,  *ceritus paribus*.

A positive coefficient for an action being conservative indicates that for
moderate respondents, an action being conservative was associated with an
increase in perceptions of it as terrorism, relative to liberal actions.  This
is a substantively large effect - almost twice the magnitude of the effect
associated with an action producing casualties.  This suggests that that
ideology has a very large effect on perceptions of terrorism - the difference
between how moderates and conservative respondents respond to an action is
almost twice as large as the average change in response associated with an
action causing casualties.  Negative interactions between the conservative
respondent and conservative action terms indicates that relative to moderate
respondents, conservative respondents found conservative actions to be much
less terroristic.

Across all models, the interactions between the liberal respondent and
conservative action terms were insignificant, indicating that liberal
respondents were not significantly different from moderate respondents in how
they reacted to conservative actions.

## Effects Graph
```{r, message=F,echo=F,warn=F}
data %>%
	ggplot(aes(x=conservative_action, y=terrorism, group=factor_ideo5, linetype=factor_ideo5)) +
	geom_smooth(aes(weight=weight_pol), col="black", method="lm") +
	ggtitle("Interaction Effects of Ideology / Conservative Action on Perceptions\nOf Terroism") +
	ylab("Perceptions of Terroism \n(Higher Scores Mean More Terroristic)") +
	xlab("Action type") +
	scale_x_discrete(labels=c( "FALSE" = "Liberal", "TRUE" = "Conservative")) +
	labs(linetype = "Respondent ideology") +
	theme_classic()

ggsave("../charts/parsanship_terrorism.png")
```

## Effects of Casualties
```{r, message=F,echo=F}
data %>%
	ggplot(aes(x=casualties, y=terrorism, group="hey")) +
	geom_smooth(aes(weight=weight_pol), col = "black", method="lm") +
	ggtitle("Relationship between Casualties on Perceptions\nOf Terrorism") +
	ylab("Terrorism \n(Higher Scores Mean More Terroristic)") +
	xlab("Action Caused Casualties") +
	theme_classic()

ggsave("../charts/casualties_terrorism.png")
```


<!---
## Partisanship on Moral Justifiability

I investigate the relationship of partisanship on perceptions of moral
justifiability, perceptions of an action as terrorism, and ratings of the
strategic usefulness of the action. As a note, the reference category for the
partisan affiliation variable is "affiliated with another party.''

## Partisanship on moral justifiability

Using a linear regression, I differences in identifying the actions as
justifiable between Republicans, Democrats, independent voters, and respondents
unsure of their partisanship relative to respondents who identify with another
party.  The results of this analysis can be seen in \autoref{p_moral_just}

I allow interactions between the effect of partisanship and whether the action
the respondent was asked about aligns with a traditionally conservative or
traditionally liberal cause.  This allows for the possibility that
Democrat-identifying respondents could be more likely to identify actions that
identify with a Republican/conservative cause as justified, and vice versa.

Across all model specifications, I find no association between a respondent
identifying as a Republican, Democrat, or Independent and their opinions of the
actions as justified.  Respondents identifying as unsure of their partisan
affiliation rate the actions as more justified, across all models.

The interactions between partisan affiliation and the ideological slant of the
actions are insignificant across all models, indicating that democrats are not
more likely to view actions in support of traditionally liberal causes as
justifiable when compared to respondents who identified with a party not
directly asked about in the survey.  The same can be said with respect to
Republicans and traditionally republican causes.

```{r, results= "asis", echo=F}
# Partisanship on Moral Justifiability
moral_just1 <- lm(moral_just ~ pid3, data = data, weights = weight_pol)
moral_just2 <- lm(moral_just ~ pid3 + conservative_action, data = data, weights = weight_pol)
moral_just3 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
moral_just4 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
moral_just5 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
moral_just6 <- lm(moral_just ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)


stargazer(moral_just1, moral_just2, moral_just3, moral_just4, moral_just5, moral_just6,
    title="Estimates of Effect of Partisanship on Moral Justifiability",
    dep.var.labels = c("Action is morally justifiable"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
	table.placement = "H",
    df=F,
	header=F,
    label = "p_moral_just"
)
```

## Effects of Partisanship on Perceptions of Actions as Strategic

In this section I test for differences in identifying actions as strategic
between Democratic, Republican, and Independent-identifying respondents
relative to respondents who chose another party.

```{r, results= "asis", echo=F}
# Partisanship on Strategic
strategic1 <- lm(strategic ~ pid3, data = data, weights = weight_pol)
strategic2 <- lm(strategic ~ pid3 + conservative_action, data = data, weights = weight_pol)
strategic3 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
strategic4 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
strategic5 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
strategic6 <- lm(strategic ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(strategic1, strategic2, strategic3, strategic4,strategic5,strategic6,
    title="Estimates of Effect of Partisanship on Strategic",
    dep.var.labels = c("Action is strategic"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
	table.placement = "H",
    df=F,
	header=F,
    label="p_strategic"
)
```

Across all models, there is a significant negative relationship between a
respondent identifying as a Republican, Democrat, or independent.  This means
that respondents identifying with these parties tended
to rate the actions as less strategic than respondents who identified with
another party, even when controlling for the effects of race and gender.

Once again, I allow for interactions between the ideological slant of an action
and the effects of partisanship, finding no significant association.  This
means that the models do not predict any difference between Republicans /
Democrats responding to a traditionally conservative / liberal action when
compared to respondents who identify with another party.

The relationship between casualties and perceptions of the actions as strategic
is uniformly negative across all models.  As the presence of casualties was
fully randomized, we can conclude that the presence of casualties directly
results in respondents rating the action as less strategic.

## Partisanship on Perception of Actions as Terrorism

In this section I test for differences in identifying actions as terrorism
between Democratic, Republican, and Independent-identifying respondents
relative to respondents who chose another party.


```{r, results= "asis", echo=F}
# Partisanship on Terrorism
terrorism1 <- lm(terrorism ~ pid3, data = data, weights = weight_pol)
terrorism2 <- lm(terrorism ~ pid3 + conservative_action, data = data, weights = weight_pol)
terrorism3 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action, data = data, weights = weight_pol)
terrorism4 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties, data = data, weights = weight_pol)
terrorism5 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties + female, data = data, weights = weight_pol)
terrorism6 <- lm(terrorism ~ pid3 + conservative_action + pid3:conservative_action + casualties + female + race, data = data, weights = weight_pol)

stargazer(terrorism1, terrorism2, terrorism3, terrorism4, terrorism5, terrorism6,
    title="Estimates of Effect of Partisanship on Terrorism",
    dep.var.labels = c("Action is terrorism"),
      covariate.labels =
          c("Democrat", "Republican","Independent",
           "Partisanship --- not sure","Conservative action", "Casualties","Female",
            "Black", "Hispanic", "Race --- other",
           "Democrat $\\times$ conserv. act.",
           "Republican $\\times$ conserv. act.",
           "Independent $\\times$ conserv. act.",
           "Not sure $\\times$ conserv. act..",
           "Intercept"),
    df=F,
	table.placement = "H",
	header=F,
    label="p_terrorism"
)
```

Across all models, there is a significant positive relationship between
respondents identifying as Democrats, and their rating the actions as
terrorism. This suggests that all else equal, Democratic respondents rated the
actions as terrorism more than those in the reference category, respondents who
identified as affiliated with a party not surveyed.

--->

