---
title: Analysis for Palestine Experiment
author: Beniamino Green
output: pdf_document
urlcolor: blue
---

# Introduction

In this document I describe the analysis I have run on the YouGov survey
investigating the effects of framing on support for assistance for the
Palestinian Authority.

The survey asked respondents to read the following passage:

> "US Secretary of State Antony Blinken visited Israel-Palestine last month after
> an 11-day escalation of violence.  After meeting with Palestinian leaders,
> Blinken announced that the US would increase assistance to the Palestinian
> Authority."

Respondents were also randomly shown one of the following sentences at the end
of the passage:

* No ending sentence (control condition)
* "A State Department official stated that increasing US assistance to
Palestinians will 'help protect American national security interests in the
region.” (National security treatment)
* "A State Department official stated that increasing US assistance to
Palestinians will 'help prevent another humanitarian crisis and civilian
suffering in the region.” (Humanitarian crisis treatment)
* "A State Department official stated that increasing US assistance to
Palestinians will 'help preserve the principles of international law in the
region.” (International law treatment)
* "A State Department official stated that increasing US assistance to
Palestinians will 'help counter racial injustice and oppression in the region.” (Racial justice)


Respondents were then asked to respond to the following three statements on a scale of strongly agree to strongly disagree.

* I would support this foreign policy decision.
* This foreign policy decision is good for American interests.
* This foreign policy decision reflects American values.

```{r load_libraries, echo=F, include=F}
# This code loads the libraries used in the analysis into memory
library(tidyverse)
library(stargazer)
```

```{r load_data, echo=F, include=F}
load("data/cleaned_data.Rdata")
load("data/models.Rdata")

```

# Measurement / Preliminaries

## Assessing the Attentive

A subset of respondents may not be reading the vignettes before answering as 20
percent of respondents read the vignettes and respond to all three questions in
under 20 seconds. A subset of respondents not reading the treatments would bias
effects towards zero those who do not read the vignettes cannot be influenced
by the treatment, diminishing the power of the experiment and increase the
chances of finding false positives.  To compensate for this, I test all
findings are consistent when analyzing the respondents of both all respondents
and attentive respondents, which I define as respondents who took more than 10
seconds to answer the survey.

```{r, results="asis", echo=F}
cleaned_data %>%
    filter(seconds_spent < 10*60) %>%
    select(seconds_spent) %>%
    data.frame() %>%
    stargazer(header=F, title="Summary Statistics: seconds spent on the survey")
```

# Analysis and Results

First, I analyze the effects of the different framings on suport for the
intervention as measured by the three questions. There are no differences in
support between treated and control respondents for all treatments except
uphold international law. Respondents who are told that the increased aid would
help uphold international law are uniformly less likely support the action, or
to identify the action as consistent with American values or interests.
Respondents exposed to the international law framing respond more negatively to
all three questions combined, indicating that this framing makes respondents
less likely to support the intervention.  I summarize these results with
representative models describing the relationship between the framing and
support as measured by the sum responses to the three questions in the survey.

```{r, results = "asis", echo=F}
stargazer(sum_all, sum_att, header=F,
          title = "Sum of responses regressed on treatment",
          column.labels=c("All respondents", "Attentive respondents"),
          dep.var.labels= "Principal Component 1",
          covariate.labels = c(
                               "Counter racial injustice",
                               "National security",
                               "Prevent humanitarian crisis",
                               "Uphold international law",
                               "Intercept"
                              )
)
```

I now investigate the effects of framings on support for aid to Palestine
including the effect of respondent ideology. I run models regressing support as
measured by each survey question, and the sum of responses to all questions.
Across all models, changing a respondent's ideology to be more liberal predicts
a significant increase in their support for intervention. Representative models
run on the sum of responses to the three questions be seen below.

```{r, results = "asis", echo=F}

stargazer(sum_treat_ideo5_dbl, sum_treat_ideo5_dbl_att, header=F,
          title = "Sum of responses to all questions regressed on treatments",
          column.labels=c("All respondents", "Attentive respondents"),
          dep.var.labels= "Sum of responses to all questions",
          covariate.labels = c(
                               "Counter racial injustice",
                               "National security",
                               "Prevent humanitarian crisis",
                               "Uphold international law",
                               "Ideology",
                               "Intercept"
                              )
)
```

I also present the relationship between respondent ideology and support for the interventions in the plot below:

```{r, include=TRUE, echo=FALSE, warn=FALSE, message=F}
cleaned_data %>%
    select(ideo5_dbl, sum) %>%
    na.omit() %>%
    ggplot(aes(x=ideo5_dbl, y=sum), na.rm=T) +
    geom_jitter(alpha=.6) +
    geom_smooth( method ="lm", se=T) +
    xlab("Respondent Ideology (Positive = Conservative)") +
    ylab("Sum of Responses to Questions") +
    ggtitle("Sum of Responses Regressed on Ideology") +
    theme_bw()


```



I then run models investigating whether there is an interaction between
ideology and the effect the treatments have on support. Put simply: "Do the
framings affect support differently among liberals and conservatives?" I
estimate models including an interaction between ideology, party, and past
voting behavior and the treatment finding no effect. However, it is an open
question as to whether this lack of an effect is due to a lack of statistical
power or the the absence of an effect.

Simulations using random data (results below) suggest that this survey design
would not be able to detect the largest interaction effect of .4, the largest
effect observed in the first YouGov survey.

```{r, echo=F}

load("data/monte_carlo_results.Rdata")

rep_sims %>% pivot_longer(c(prop_significant, prop_negative,
                            exaggeration_factor),names_to="statistic")  %>%
    mutate(statistic = statistic %>%
           recode(
                  exaggeration_factor="Exaggeration Factor",
                  prop_negative="Type S error rate",
                  prop_significant="Power",
                  )) %>%
    ggplot(aes(x=effect_size, y=value, col=statistic)) +
    theme_bw()  +
    geom_line() +
    facet_wrap(~statistic, scales="free") +
    ggtitle("Replipicability Measures by Effect Size") +
    theme(legend.position = "none") +
    geom_vline(xintercept = .4, linetype=2, col="grey") +
    xlab("Effect Size") +
    ylab("Value")

sample_size_sims %>%
    ggplot(aes(x=sample_size, y=prop_significant)) +
    geom_line() +
    geom_hline(yintercept=.8, linetype=2, color="grey") +
    ggtitle("Power to Detect Interaction Effect by Sample Size") +
    xlab("Sample Size") +
    ylab("Statistical Power") +
    theme_bw()

```
