---
title: YouGov Survey Data Analysis
author: Author Name
output: pdf_document
urlcolor: blue
---

```{r load_libraries, echo=F, include=F}
# This code loads the libraries used in the analysis into memory
library(tidyverse)
library(stargazer)
```

# Introduction

In this document, I describe the analysis I have run on the YouGov survey
investigating the effects of "woke" framings on support for congressional action on an a set of issues.

Respondents to the survey were shown one of the following 6 statements:

* Congress is negotiating a bill to address issues raised by Latinx communities.
* Congress is negotiating a bill to address issues raised by Hispanic/Latino communities.
* Congress is negotiating a bill to address issues raised by communities of color.
* Congress is negotiating a bill to address issues raised by racial minorities.
* Congress is negotiating a bill to address issues raised by the Black Lives Matter movement.
* Congress is negotiating a bill to address issues raised by recent protests for racial equality.

Respondents were then asked to respond to the following three statements on a scale of "strongly disagree" to "strongly agree."

1. I would support Congress passing a bill to address these issues.
2. These issues are important to me.
3. These issues are important for American society.


## Preliminaries:

As was the case with the Palestine survey, a subset of respondents appear to
not be reading the vignettes / questions before they respond. This would
decrease the observable treatment effect, and make it more likely that a
significant result is due to chance alone. I run all models discussed in this
analysis on all respondents, and on the subset of respondents who took more
than 10 seconds to respond to the survey, to ensure that the results are not
dependent on the inclusion of respondents who were not exposed to the
treatment.

```{r, results="asis", echo=F}
cleaned_data %>%
    filter(seconds_spent < 10*60) %>%
    select(seconds_spent) %>%
    data.frame() %>%
    stargazer(header=F, title="Summary Statistics: Seconds spent on the survey")
```

```{r load_data, echo=F, include=F}
load("data/cleaned_data.Rdata")
load("data/estimated_models.Rdata")
```

I create a set of principal components which summarize responses to the three measures. The loadings for these components can be seen below:

# PCA
```{r, results="asis", echo=F}

rownames(pca$rotation) <- c("I would support Congress adressing this issue",
                   "These issues are important to American society",
                   "These issues are important to me")


pca$rotation %>%
    data.frame() %>%
    stargazer(summary=F, title="Prinicipal Component Loadings", header=F)

```

The first principal component explains roughly 90% of the variance responses to
the question, suggesting that it well explains most of the variation in the
data. It is strongly negatively correlated with responses to all three
questions suggesting that it encodes a respondent's general support for the
proposed congressional action, where more positive values indicate respondents
that are less enthusiastic about the bill.

# Analysis


I first analyze the effects of changing a framing from "non-woke" to "woke"
across all respondents. The coefficient for "woke" is uniformly negative among
both all and attentive respondents. This suggests that changing the framing of
an issue from "non-woke" to "woke" is associated with a significant decrease in
support. This effect can also be seen when examining responses to the three
questions individually. Across all questions, changing a framing from
"non-woke" to "woke" significantly decreases support and perceptions of the
bill as important.

```{r, results="asis", echo=F}
stargazer(pca_woke, pca_woke_att,
          title = "principal component (negative = supportive) on woke framing",
          dep.var.labels= "Principal Component 1",
          covariate.labels = c("Woke", "Intercept"),
          header=F)
```

I then include an effect for a respondent's ideology, and allow the effect of
"woke" framings to vary between respondents of different ideologies. A
significant positive coefficient for a respondents' ideology indicates that
liberal respondents view all congressional actions more favorably. The
coefficient for the interaction between woke and a respondents' ideology is
positive, but not significant at conventional levels (p<.1), suggesting that
liberal respondents may respond more positively to woke framings, but the
evidence is ambivalent.

```{r results="asis", echo=F}
stargazer(pca_woke_x_ideo5_dbl, pca_woke_x_ideo5_dbl_att,
          header = F,
          title = "principal component (negative = supportive) on woke framing",
          dep.var.labels= "Principal Component 1",
          covariate.labels = c("Woke","Ideology","Woke X Ideology", "Intercept")

)
```

Similar to the results from the Palestine survey experiment, interactions
between treatment and respondents' ideology and past voting are not significant
at conventional significance levels. This result is consistent across all
measures of ideology and party affiliation, indicating that a respondents'
party, ideology, and past voting had no effect on how they responded to a
framing being "woke" or not.
