---
title: YouGov Survey Data Analysis
author: Beniamino Green
output: pdf_document
urlcolor: blue
header-includes:
   - \usepackage{float}
---

```{r load_libraries, echo=F, include=F}
# This code loads the libraries used in the analysis into memory
library(tidyverse)
library(stargazer)

load("data/cleaned_data.Rdata")
load("data/estimated_models.Rdata")

```

# Introduction

In this document, I describe the analysis I have run on the YouGov survey
investigating the effects of "woke" framings on support for congressional action on an a set of issues.

Respondents to the survey were shown one of the following 6 statements:

* Congress is negotiating a bill to address issues raised by Latinx communities.
* Congress is negotiating a bill to address issues raised by Hispanic/Latino communities.
* Congress is negotiating a bill to address issues raised by communities of color.
* Congress is negotiating a bill to address issues raised by racial minorities.
* Congress is negotiating a bill to address issues raised by the Black Lives Matter movement.
* Congress is negotiating a bill to address issues raised by recent protests for racial equality.

Respondents were then asked to respond to the following three statements on a scale of "strongly disagree" to "strongly agree."

1. I would support Congress passing a bill to address these issues.
2. These issues are important to me.
3. These issues are important for American society.

I give a breakdown for the answers to these questions below. The columns in the
table show the question being asked, and the rows give the response. Each cell
value gives the fraction of respondents who answered with the given response to
the question. Tables 2 and 3 show this same information for respondents exposed
to woke and non-woke framings respectively.

```{r, echo = F, results = "asis"}

cross_tabler <-function(df)
{
    df %>%
    select(personally_important, nationally_important, support) %>%
    pivot_longer(everything(), names_to = "question") %>%
    group_by(question, value) %>%
    tally() %>%
    pivot_wider(names_from = question, values_from = n) %>%
    mutate(
        nationally_important = nationally_important / sum(nationally_important),
        personally_important = personally_important / sum(personally_important),
        support = support / sum(support),
        value = value %>%
            dplyr::recode(
                `-3` = "Strongly Disagree",
                `-2` = "Disagree",
                `-1` = "Somewhat Disagree",
                `0` = "Neutral",
                `1` = "Somewhat Agree",
                `2` = "Agree",
                `3` = "Strongly Agree"
            )
    ) %>%
    data.frame() %>%
    mutate_at(
              c("personally_important", "nationally_important", "support"),
              ~ paste0(round(.x*100,2), "%"))

}

cleaned_data %>%
    cross_tabler() %>%
    stargazer(
        header = F,
          table.placement = "H",
        summary = F,
        rownames=F,
        title="Table of responses to survey questions for respondents exposed to all framings",
        covariate.labels = c("Response", "Personally Important", "Nationally
                             Important", "Support")
    )

cleaned_data %>%
    filter(woke) %>%
    cross_tabler() %>%
    stargazer(
        header = F,
          table.placement = "H",
        summary = F,
        rownames=F,
        title="Table of responses to survey questions for respondents exposed to woke framings",
        covariate.labels = c("Response", "Personally Important", "Nationally
                             Important", "Support")
    )

cleaned_data %>%
    filter(!woke) %>%
    cross_tabler() %>%
    stargazer(
        header = F,
          table.placement = "H",
        summary = F,
        rownames=F,
        title="Table of responses to survey questions for respondents exposed to non-woke framings",
        covariate.labels = c("Response", "Personally Important", "Nationally
                             Important", "Support")
    )

```

I also give summary statistics for each question, showing the mean answer on a
scale of -3 to 3 (positive = agree), as well as the standard deviation, and
$25^{th}$ and $75^{th}$ percentile responses.

```{r, results = "asis", echo = F}

cleaned_data %>%
    select(personally_important, nationally_important, support) %>%
    data.frame() %>%
    stargazer(
              header = F,
              table.placement = "H",
              title = "Summary Statistics: Responses By Question Asked",
              covariate.labels=c('Personally Important','Nationally Important','Support')
    )

```

For the main models in the paper, I summed responses these three questions into
a single variable encoding general support. This variable ranges from -9 to 9,
and has a mean of 2.03 and standard deviation of 5.694. I provide this
information in a tabular format in table 2:

```{r, results = "asis", echo = F}
cleaned_data %>%
    select(sum) %>%
    data.frame() %>%
    stargazer(
              table.placement = "H",
              header = F,
              covariate.labels = "Summed Responses",
              title = "Summary Statistics: Sum of Responses"
    )
```

I also provide a histogram showing the overall distribution of this outcome
variable:

```{r, echo = F}
cleaned_data %>%
    ggplot(aes(x=sum)) +
    geom_histogram(binwidth=1) +
    theme_bw() +
    xlab("Sum of Responses to all Questions") +
    ylab("Count of Respondents") +
    ggtitle("Distribution of Summed Responses to Survey Questions")
```


# Assessing the Attentive

As was the case with the Palestine survey, a subset of respondents appear to
not be reading the vignettes / questions before they respond. This would
decrease the observable treatment effect, and make it more likely that a
significant result is due to chance alone. I run all models discussed in this
analysis on all respondents, and on the subset of respondents who took more
than 10 seconds to respond to the survey, to ensure that the results are not
dependent on the inclusion of respondents who were not exposed to the
treatment.

```{r, results="asis", echo=F}


cleaned_data %>%
    filter(seconds_spent < 10*60) %>%
    select(seconds_spent) %>%
    data.frame() %>%
    stargazer(header=F,
          table.placement = "H",
          title="Summary Statistics: Seconds spent on the survey"
    )
```


# Analysis

I first analyze the effects of changing a framing from "non-woke" to "woke"
across all respondents. The coefficient for "woke" is uniformly negative among
both all and attentive respondents. This suggests that changing the framing of
an issue from "non-woke" to "woke" is associated with a significant decrease in
support across all questions. This effect is also present when examining
responses to the three questions individually. Across all questions, changing a
framing from "non-woke" to "woke" significantly decreases support and
perceptions of the bill as important.

```{r, results="asis", echo=F}
#cat("\\setcounter{table}{0}")

stargazer(sum_woke, sum_woke_att,
          title = "Sum of answers of questions on woke framing",
          dep.var.labels= "Sum of Answers",
          covariate.labels = c("Woke", "Intercept"),
          table.placement = "H",
          header=F)
```

I also display this information in a boxplot, showing the sum of answers to the
survey questions for respondents exposed to the woke and non-woke framings.

```{r, include=TRUE, echo=FALSE, message=F}

library(ggsignif)
library(tidyverse)

cleaned_data %>%
    mutate(woke = ifelse(woke, "Woke", "Non-woke")) %>%
    ggplot(aes(x=woke, y=sum)) +
    geom_boxplot() +
    geom_signif(comparisons = list(c("Woke", "Non-woke")),
                test="t.test",
                map_signif_level = TRUE) +
    ggtitle("Average Support by Framing") +
    xlab("Woke / non woke framing") +
    ylab("Sum of responses to 3 questions") +
    theme_bw() +
    coord_cartesian(ylim = c(-1, 10))

```

I then include an effect for a respondent's ideology, and allow the effect of
"woke" framing to vary between respondents of different ideologies. A
significant negative coefficient for a respondents' ideology indicates that
liberal respondents view all congressional actions more favorably. The
coefficient for the interaction between woke and a respondents' ideology is
positive, but not significant at conventional levels (p<.1), suggesting that
liberal respondents may respond more positively to woke framing, but the
evidence is ambivalent.

```{r results="asis", echo=F}

stargazer(sum_woke_x_ideo5_dbl, sum_woke_x_ideo5_dbl_att,
          header = F,
          table.placement = "H",
          title = "Sum of responses to survey questions on woke framing",
          dep.var.labels= "Sum of Responses",
          column.labels = c("All Respondents", "Attentive Respondents"),
          covariate.labels = c("Woke","Ideology","Woke X Ideology", "Intercept")

)
```

Similar to the results from the Palestine survey experiment, interactions
between treatment and respondents' ideology and past voting are not significant
at conventional significance levels. This result is consistent across all
measures of ideology and party affiliation, indicating that a respondents'
party, ideology, and past voting had no effect on how they responded to a
framing being "woke" or not.


# Appendix:

## Models for Effect of Woke Framing Among Respondents Exposed to Each Condition

Finally, I provide models showing the effect of the woke framing among
respondents exposed to each individual condition. Table 3 shows the effect of a
woke framing on support for only respondents exposed to questions about Latino
communities. Tables 4 and 5 show the effects of a woke framing on respondents
only exposed to the BLM questions or racial equality questions, respectively.

```{r, echo=F, results = "asis"}

stargazer(
          title = "Support among respondents exposed to Latino communities question",
          sum_woke_latino, sum_woke_ideo5_latino,
          sum_woke_x_ideo5_latino,
          covariate.labels = c(
               "Woke", "Ideology",
               "Woke X Ideology", "Intercept"
           ),
          header = F,
          table.placement = "H",
          dep.var.labels= "Sum of Responses")

```

```{r, echo=F, results = "asis"}

stargazer(
          title = "Support among respondents exposed to BLM question",
          sum_woke_blm, sum_woke_ideo5_blm,
          sum_woke_x_ideo5_blm,
          covariate.labels = c(
               "Woke", "Ideology",
               "Woke X Ideology", "Intercept"
           ),
          header = F,
          table.placement = "H",
          dep.var.labels= "Sum of Responses")

```

```{r, echo=F, results = "asis"}

stargazer(
          title = "Support among respondents exposed to racial equality question",
          sum_woke_racial, sum_woke_ideo5_racial,
          sum_woke_x_ideo5_racial,
          covariate.labels = c(
               "Woke", "Ideology",
               "Woke X Ideology", "Intercept"
           ),
          header = F,
          table.placement = "H",
          dep.var.labels= "Sum of Responses")

```

